%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Tasker} % Job title
    {RemoTasks} % Organization
    {Remote} % Location
    {Oct. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {Bulba Extensions - Compared the code output and execution steps between varying AI model responses for safety, accuracy, and fulfillment. Lots of Googling to ensure the responses were accurate and not hallucinations. Wrote summaries for each explaining any differentiating factors or key details about accuracy, fulfillment, and/or verbosity.}
		  \item {LiDAR - Analyzed data collected from autonomous vehicle sytems to identify their surroundings in image format and in Lidar-mapped nodes. Workflow consisted of detecting pedestrian/automotive territory, hazards, and authorities.}
		  \item {Intravascular ultrasound Annotation - Reviewed video data from a catheter to train an AI to detect and distinguish veins, arteries, stents, and blood clots in the human body. Workflow was mostly frame-by-frame outlining.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Warehouse Associate} % Job title
    {Costco Wholesale} % Organization
    {Fresno, California} % Location
    {Nov. 2017 - Mar. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  \item {Utilized in many departments (10+) for great member service and and positive attitude. Always on the leaderboard in cashiering, and constantly performing supervisorly tasks for other cashiers. I was often asked to use the inventory terminal to look up members and items because of my fast typing speed. A part of using the terminal was inventory tracking bewteween locations and making porduct signs. }
	  \item {In Sales I managed phone calls in the office and on the floor, offering product information about cellphones, televisions, speakers, and more. Being on the floor, I was the first person to call whenever someone needed assistance with a bulky load. I was also effective at stocking inventory and maintaining pallets in my aisles.} 
	  \item {Operated and managed the equipment and inventory of the photo lab. Assisted members with photo orders and device difficulties.}
	  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
