%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}


% Hello! I'm Tim, passionate software dev with 15+ years of experience specializing in software, architecture, mechanics, design, and more. I'm looking forward to contribute to something great. I enjoy helping people and solving problems and see myself working in IT because I love sharing what I know.

% Absolutely LOVE Vim, even in my terminal and in VScode. I love open source projects and love participating in community forums and discussions to better myself and others for the pursuit of knowledge. Comfortable with daily drivers Windows and Linux, but okay with macOS. Super nerd that loves Vim mode and my custom dotfiles so I  can develop fast and efficiantly. Always making sure my setup is customized  to find the most optimal environment. Interested in devising a better problem-solving method for challenging tasks, and learning new technologies and tools.

% I'm looking forward to apply my skills and expertise to a challenging and dynamic role, ideally in IT support or software development, where I can continue to grow and make a meaningful impact in the world of tech.

%---------------------------------------------------------
Timothy is a passionate freelancer with over a decade of experience in the industry. Specializing in CX, programming, mechanics, and design, Timothy is constantly looking forward to contributing his skills to new opportunities in the tech world. Whether it's helping people or attacking challenges, Timothy sees himself working in IT because it's what he loves to do.

He's a super nerd who absolutely loves modal editors like Vim, his fine-tuned personalized dotfiles, and can't see himself working with less than two monitors. His passion for open source projects and community participation gives him the freedom to be creative and think of new projects. ons to better myself and others for the pursuit of knowledge. Comfortable with daily drivers Windows and Linux, and semi-comfy with macOS. Despite this, Timothy is always pursuing knowledge to better himself and others.

Timothy is looking forward to apply his skills and expertise to a challenging and dynamic role, ideally in IT or CX, where he can continue to grow and make a meaningful impact on the world around him. Connect with him to see how he can contribute to your team!
\end{cvparagraph}
